\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Test Automation Engineer \hfill 11 2019 --- Present}}
\subtext{KENDAXA Development s.r.o. \hfill Prague, Czechia}
\begin{zitemize}
\item Designing and automating end-to-end test scenarios using Cypress and TypeScript.
\item Documenting the testing process and writing test cases with TestLink.
\item Manages the testing of multiple projects of significant complexity.
\item Possess thorough technical and operational knowledge within the QA area of responsibility.
\item Assist Application Developers and technical support staff in identifying and resolving defects.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Project - Term Paper Catalogue \hfill 09 2019 --- 05 2020}}
\subtext{High School \hfill Prague, Czechia}
\begin{zitemize}
\item Full-Stack project (Front-End, Back-End, MySQL DB implementation)
\item Online catalogue for term parers. Featuring search, user system, automatic keyword extraction from paper abstract.
\item Back-End written in Node.js using express, with custom middle-ware for parsing uploaded PDFs
\item Front-End written in React JS, with CSS (Of course!)
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Independent Financial Coach \hfill 06 2021 --- 04 2022}}
\subtext{Partners Financial Services, a.s. \hfill Prague, Czechia}
\begin{zitemize}
\item Deliver financial advice to clients, proposing strategies to achieve short- and long-term objectives\\ for investments, insurance, business and estate planning with minimal risk.
\item Basic team management skills.
\item Great improvement to the communications skills, in-person or over the phone.
\end{zitemize}
\end{document}